My title

### 2024-11-04 paper/paper.qmd
Added to appendix

>>>>

Non-response refers to missing data in a dataset when respondents either skip specific questions, groups of questions, or even refuse to participate entirely. Non-response from individuals introduces sampling error, as it may lead to biases in the results if certain population segments are underrepresented. Government statistics are generally reliable but must be viewed critically, especially considering the potential for political influences, methodological limitations, or errors. Despite this, when methodologies are transparent and data is subjected to independent audits, government statistics can still serve as valuable sources of information for policy research, but users should always be aware of potential biases and limitations.
